Lab 6 - Diagnostics and simulation based inferences: Answers

### 2023-02-22 Lab 6  Diagnostics and simulation based inferences/Lab6_Simulation_Uncertainty.Rmd
Add files via upload

---
title: "Lab 6 - Diagnostics and simulation based inferences "
author: "Eric Parajon"
output: pdf_document
---

@@

Today, we will use simulation to help us assess the uncertainty around our parameter estimates and will then incorporate this uncertainty into the predicted values of our outcome variable.

We will be examining **Regression Diagnostics**, or ways to examine if our regression meets necessary assumptions, and if anything weird (e.g., outliers, etc.) is going on. Remember the four key assumptions of a linear regression:

@@

Download the "aid_data_95_ee.csv" in the Labs folder on Sakai and then read it into R:
```{r, warning = F, message = F}
#remember to set your working directory!
setwd("______")

@@

  theme_bw()
  #theme
```
# Regression Diagnostics

@@

And last but not least, you can use the performance package (and the see package) to generate really nicely formatted regression assumption plots!
```{r}
pacman::p_load(see,
               performance)

@@

#confidence intervals
t(apply(____, 2, quantile, prob = c(.1, .9)))
confint(guns_model, ____)

@@

#hypothetical predictor matrix
 X_sim_guns <- with(Guns,
                   model.matrix(~ ____,
                      data = data.frame(male = mean(male),
                                        income = mean(income),
                                        law = c(____),
                                        density = rep(density_sim, each = 2))
                   ))

@@

pred_df_guns <- data.frame(PP = robbery_hat_quant[2, ],
                      UB = robbery_hat_quant[3, ],
                      LB = robbery_hat_quant[1, ],
                      Density = X_sim_guns[, "density"],
                      Law = c("No", "Yes")[X_sim_guns[, "law"] + 1])

ggplot(data =____) +
  geom_ribbon(aes(____fill = Law), alpha = 0.5) +
  geom_line()

>>>>

---
title: "Lab 6 - Diagnostics and simulation based inferences "
author: "Eric Parajon"
output:
  html_document:
    df_print: paged
---

@@

Today, we will use **simulation** to help us assess the uncertainty around our parameter estimates and will then incorporate this uncertainty into the predicted values of our outcome variable.

We will be also be examining **Regression Diagnostics**, or ways to examine if our regression meets necessary assumptions, and if anything weird (e.g., outliers, etc.) is going on. Remember the four key assumptions of a linear regression:

@@

Download the "aid_data_95_ee.csv" in the Labs folder on Canvas and then read it into R:
```{r, warning = F, message = F}
#remember to set your working directory!
#setwd("______")

@@

  theme_bw()
  #theme
```
# Regression Diagnostics
Next we turn to another important topic evaluating your regressions!

@@

And last but not least, you can use the performance package (and the see package) to generate really nicely formatted regression assumption plots!
```{r,fig.width=10, fig.height=7}
pacman::p_load(see,
               performance)

@@

#confidence intervals (showing both methods)
t(apply(____, 2, quantile, prob = c(.1, .9)))
confint(guns_model, ____)

@@

#hypothetical predictor matrix
 X_sim_guns <- with(Guns,
                   model.matrix(~ ____,
                      data = data.frame(male = mean(male),
                                        income = mean(income),
                                        law = c(____),
                                        density = rep(density_sim, each = 2))
                   ))
 ## Compute point estimates (estimation uncertainty)

@@

#Creating prediction df
pred_df_guns <- data.frame(PP = robbery_hat_quant[2, ],
                      UB = robbery_hat_quant[3, ],
                      LB = robbery_hat_quant[1, ],
                      Density = X_sim_guns[, "density"],
                      Law = c("No", "Yes")[X_sim_guns[, "law"] + 1])

#Plotting
ggplot(data =____) +
  geom_ribbon(aes(____fill = Law), alpha = 0.5) +
  geom_line()+
  xlab("____") +
  ylab("____") +
  theme_bw()

### 2023-02-22 Lab 6  Diagnostics and simulation based inferences/Lab6_Simulation_Uncertainty_Answers.Rmd
Add files via upload

---
title: "Lab 6 - Diagnostics and simulation based inferences: Answers"
author: "TA: Eric Parajon"
output: pdf_document
---

@@

Today, we will use simulation to help us assess the uncertainty around our parameter estimates and will then incorporate this uncertainty into the predicted values of our outcome variable.

```{r}
#clear global environ
rm(list=ls())

@@

Download the "aid_data_95_ee.csv" in the Labs folder on Sakai and then read it into R:
```{r, warning = F, message = F}
#remember to set your working directory!

@@

set.seed(53)

@@

#confidence intervals
t(apply(samp_beta_guns, 2, quantile, prob = c(.1, .9)))
confint(guns_model, level = .8)

@@

@@

pred_df_guns <- data.frame(PP = robbery_hat_quant[2, ],
                      UB = robbery_hat_quant[3, ],
                      LB = robbery_hat_quant[1, ],
                      Density = X_sim_guns[, "density"],
                      Law = c("No", "Yes")[X_sim_guns[, "law"] + 1]) #why can we do this?  `

ggplot(data = pred_df_guns, aes(x = Density, y = PP, lty = Law)) +
  geom_ribbon(aes(ymin = LB, ymax = UB, fill = Law), alpha = 0.5) +
  geom_line() + #what do you think this does?
  xlab("Population Density") +
  ylab("Predicted Number of Robberies") +
  theme_bw()

>>>>

---
title: "Lab 6 - Diagnostics and simulation based inferences: Answers"
author: "Eric Parajon"
output:
  html_document:
    df_print: paged
---

@@

Today, we will use **simulation** to help us assess the uncertainty around our parameter estimates and will then incorporate this uncertainty into the predicted values of our outcome variable.

We will be also be examining **Regression Diagnostics**, or ways to examine if our regression meets necessary assumptions, and if anything weird (e.g., outliers, etc.) is going on. Remember the four key assumptions of a linear regression:

1) Linearity of the data - the relationship between x and y is linear

2) Normality of residuals - the residual errors are normally distributed

3) Homogeneity of residual variance - the residuals have CONSTANT variance (homoscedasticity)

4) Independence of residual error terms

The following tests will help us see if these assumptions hold, and will examine a number of possible issues. These include (but are not limited to) non-linearity of the data, heteroscedasticity (non-constant variance in the errors), and presence of influential values (outliers and high-leverage points).

```{r, message = FALSE}
#clear global environ
rm(list=ls())

@@

Download the "aid_data_95_ee.csv" in the Labs folder on Canvas and then read it into R:
```{r, warning = F, message = F}
#remember to set your working directory!

@@

set.seed(123)

@@

#confidence intervals
  #Method 1
t(apply(samp_beta_guns, 2, quantile, prob = c(.1, .9)))
  #Method 2
CI<-confint(guns_model, level = .8)

CI

#Now doing the Monte Carlo inference for average prediction
# to get the predicted robbery rate as the population density varies from its 10th percentile to its 90th percentile dependent on if a shall carry law is in effect

@@

 ## Compute point estimates (estimation uncertainty)

@@

#Creating prediction df

pred_df_guns <- data.frame(PP = robbery_hat_quant[2, ],
                      UB = robbery_hat_quant[3, ],
                      LB = robbery_hat_quant[1, ],
                      Density = X_sim_guns[, "density"],
                      Law = c("No", "Yes")[X_sim_guns[, "law"] + 1]) 
#Plotting

ggplot(data = pred_df_guns, aes(x = Density, y = PP, lty = Law)) +
  geom_ribbon(aes(ymin = LB, ymax = UB, fill = Law), alpha = 0.5) +
  geom_line() + 
  xlab("Population Density") +
  ylab("Predicted Number of Robberies") +
  theme_bw()
